Binary companions of red giant stars in \apogee\ \DR

### 2018-02-27 paper/1-catalog/twoface-catalog.tex
Caption for infer jitter

\begin{table}[h!]
    \centering
    \begin{tabular}{ r c l }
    \hline
    name & prior & description \\
    \hline
    $P$ & $\ln P \sim \mathcal{U}(1, 32768)~\textrm{day}$ & period \\
    $e$ & $e \sim \textrm{Beta}(0.867, 3.03)$ & eccentricity \\
    $t_0$ & fixed & reference time \\
    $M_0$ & $M_0 \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & mean anomaly at reference time \\
    $\omega$ & $\omega \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & argument of pericenter \\
    $s^2$ & $\ln s^2 \sim \mathcal{N}(\mu_y, \sigma_y^2)$ & extra variance added to each visit variance \\
    $K$ & $\mathcal{N}(0, \sigma_{v}^2)~\kms$ & velocity semi-amplitude \\
    $v_0$ & $\mathcal{N}(0, \sigma_{v}^2)~\kms$ & system barycentric velocity \\
    \hline
    \end{tabular}
    \caption{Summary and description of parameters. $\textrm{Beta}(a, b)$ is the
    beta distribution with shape parameters $(a, b)$, $\mathcal{U}(a, b)$ the
    uniform distribution over the domain $(a, b)$, and $\mathcal{N}(\mu,
    \sigma^2)$ is the normal distribution with mean $\mu$ and variance
    $\sigma^2$.
    For the systemic velocity and semi-amplitude, $(v_0, K)$, we use a broad
    Gaussian prior that is formally inconsistent between \thejoker\ and
    follow-up MCMC sampling (see \sectionname~\ref{sec:mcmc}): in \thejoker\ we
    assume Gaussian priors with $\sigma_v$ much larger than the measurement
    uncertainty so they can be neglected ($\sigma_v \approx \infty$), whereas
    when running MCMC we fix $\sigma_v = 10^3~\kms$.}
    \label{tbl:params}
\end{table}

@@

\todo{Fix this bit from copy-pasting}

A full run of \thejoker\ on all \nstars\ \apogee\ stars used in this work took
approximately 300 hours on a compute cluster with 448 cores, with the time
dominated by sources with many ($\gtrsim 10$) visits.

For this initial run, we do not follow up on stars that return $<$\nposterior\
samples.

of the initial distribution set to $(\mu_{y,0}, \sigma_{y,0})
= (10.6, 3)$ in units of $\textrm{m}~\textrm{s}^{-1}$.

@@

We use 1,825 stars with $>10$ visits and $\log g < 2$ (to avoid upper RGB stars
that have large intrinsic jitter) and maximize the above likelihood to determine
better hyperparameters for the log-excess-variance parameter distribution.
\figurename~\ref{fig:infer-jitter} shows the distribution corresponding to the
maximum-likelihood hyperparameters, $\alpha^* = (\mu_y^*, \sigma_y^*) = (9.50,
1.64)$.
\todo{Reactions to the inferred parameters?}

% Notebook: "Infer jitter"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{infer-jitter}
\end{center}
\caption{%
\todo{move notebook to figures path, re-do with "run2" or "run1" samples...}
Inferred prior over log-jitter parameter ($y = \ln s^2$) using posterior samples
for 1,825 lower-RGB stars with $>10$ visits.
Left panel shows the ... Right panel shows the ...
\label{fig:infer-jitter}
}
\end{figure}

@@

Using the maximum-likelihood hyperparameters derived from the initial posterior
samplings (see \sectionname~\ref{sec:inferjitter}), we update and fix the
excess variance prior distribution parameters---$(\mu_{y}, \sigma_{y}) = (9.5,
1.6)$, in units of $\textrm{m}~\textrm{s}^{-1}$---and re-run \thejoker\ on the
parent sample of \apogee\ \DR\ stars.
\todo{Discuss how this relates to empirical Bayes?}

>>>>

\begin{table}[h]
    \centering
    \begin{tabular}{ r l l }
    \hline
    name & prior & description \\
    \hline
    $P$ & $\ln P \sim \mathcal{U}(1, 32768)~\textrm{day}$ & period \\
    $e$ & $e \sim \textrm{Beta}(0.867, 3.03)$ & eccentricity \\
    $t_0$ & fixed & reference time \\
    $M_0$ & $M_0 \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & mean anomaly at reference time \\
    $\omega$ & $\omega \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & argument of pericenter \\
    $s^2$ & $\ln s^2 \sim \mathcal{N}(\mu_y, \sigma_y^2)$ & extra variance added to each visit variance \\
    $K$ & $\mathcal{N}(0, \sigma_{v}^2)~\kms$ & velocity semi-amplitude \\
    $v_0$ & $\mathcal{N}(0, \sigma_{v}^2)~\kms$ & system barycentric velocity \\
    \hline
    \end{tabular}
    \caption{Summary and description of parameters. $\textrm{Beta}(a, b)$ is the
    beta distribution with shape parameters $(a, b)$, $\mathcal{U}(a, b)$ the
    uniform distribution over the domain $(a, b)$, and $\mathcal{N}(\mu,
    \sigma^2)$ is the normal distribution with mean $\mu$ and variance
    $\sigma^2$.
    For the systemic velocity and semi-amplitude, $(v_0, K)$, we use a broad
    Gaussian prior that is formally inconsistent between \thejoker\ and
    follow-up MCMC sampling (see \sectionname~\ref{sec:mcmc}): in \thejoker\ we
    assume Gaussian priors with $\sigma_v$ much larger than the measurement
    uncertainty so they can be neglected ($\sigma_v \approx \infty$), whereas
    when running MCMC we fix $\sigma_v = 10^3~\kms$.}
    \label{tbl:params}
\end{table}

@@

@@

We execute a full run of \thejoker\ on all \nstars\ \apogee\ stars in our parent
sample using initial values for the excess variance distribution parameters
chosen so that $\sqrt{e^{\mu_{y,0}}} \approx 200~\mps$: $(\mu_{y,0},
\sigma_{y,0}) = (10.6, 3)$ in units of $\mps$.
This run took approximately 300 hours on a compute cluster with 448 cores, with
the time dominated by sources with many ($\gtrsim 10$) visits.  For this initial
run, we do not follow up on stars that return $<$\nposterior\ samples.

We use 1,825 stars with $>10$ visits and $\log g < 2$ (to avoid upper RGB stars
that have large intrinsic jitter) and maximize the above likelihood to determine
better hyperparameters for the log-excess-variance parameter distribution.
\figurename~\ref{fig:infer-jitter} shows the distribution corresponding to the
maximum-likelihood hyperparameters, $\alpha^* = (\mu_y^*, \sigma_y^*) = (9.50,
1.64)$.
These values are consistent with the estimated systematic floor of the visit
velocity uncertainties of $\approx 100$--$200~\mps$ estimated from stars
observed multiple times and on multiple plates (\citealt{Nidever:2015}).

However, there are a number of caveats to keep in mind about this estimate of
the excess variance distribution.
First, we do not remove triple or other multiple systems: For any individual
system, the radial velocity variations induced by other massive bodies will lead
to larger preferred values for the excess variance parameter.
We don't expect there to be a large number of triple systems in our sample, but
this is still an important consideration for future efforts.
Second, we are sensitive to outliers and very non-Gaussian systematic error
distributions.
In fact, the residuals we find away from our best-fit two-body orbital solutions
do not appear strictly Gaussian and have tails towards larger systematic errors.
\figurename~\ref{fig:residuals} shows the distribution of normalized residuals,
$R_{nk}$, for each visit: the $k$ visit velocities for each $n$ star, $v_{nk}$,
minus the predicted radial velocity from the best-fitting sample returned by
\thejoker, $\hat{v}^*_{nk}$, normalized by the excess-variance-included
uncertainty, $\sigma_{nk}^* = \sqrt{\sigma_{nk}^2 + \hat{s}_{n}^2}$, where
$\hat{s}_{n}$ is computed from the excess-variance parameter of the best-fitting
sample:
\begin{equation}
    R_{nk} = \frac{v_{nk} - \hat{v}^*_{nk}}{\sqrt{\sigma_{nk}^2 +
    \hat{s}_{n}^2}} \quad .
\end{equation}

% Notebook: "Infer jitter"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{infer-jitter}
\end{center}
\caption{%
Inferred prior over excess variance parameter ($y = \ln s^2$) using posterior
samples for 1,825 lower-RGB stars with $>10$ visits.
Left and right panels show the distribution corresponding to the
maximum-likelihood parameters $(\mu_y, \sigma_y) = (9.50, 1.64)$ in log and
linear, respectively.
\label{fig:infer-jitter}
}
\end{figure}

% Notebook: "Residuals-vs-metadata"
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{residuals}
% \end{center}
% \caption{%
% \todo{stuff}
% \label{fig:residuals}
% }
% \end{figure}

@@

Using the maximum-likelihood hyperparameters derived from the initial posterior
samplings (see \sectionname~\ref{sec:inferjitter}), we update and fix the
excess variance prior distribution parameters---$(\mu_{y}, \sigma_{y}) = (9.50,
1.64)$, in units of $\textrm{m}~\textrm{s}^{-1}$---and re-run \thejoker\ on the
parent sample of \apogee\ \DR\ stars.
\todo{Discuss how this relates to empirical Bayes?}
